Simulation Results

### 2021-05-07 simulation-results/Simulation Results.Rmd

---
title: "Simulation Results"
author: "Evan Miyakawa"
output: pdf_document
---

@@

```{r}
exp_gamma_bench_files <- c(
  here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-results.rds"),
  here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-results-greta.rds"),
  here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-results-stan.rds")
)

@@

```{r}
# bench_results <- bind_rows(
#   exp_gamma_results,
#   normal_gamma_tau_results,
#   normal_normal_results,
#   beta_bernoulli_results, 
#   beta_binomial_results,
#   poisson_gamma_results,
#   hier_beta_binomial_results,
#   hier_full_bb_results,
#   hier_log_reg_results,
#   linear_reg_results,
#   logistic_reg_results,
#   poisson_reg_results
# )
# 
# bench_results
# 
# saveRDS(bench_results, file = "bench_results.RDS")

@@

# saveRDS(bench_results_indiv, file = "bench_results_indiv.RDS")
# saveRDS(bench_results_indiv, file = "bench_results_indiv2.RDS")
```

@@

## Strip Charts

```{r}
bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  ggplot(aes(method, time)) + 
  geom_jitter(width = 0.1) + 
  facet_wrap(vars(model)) + 
  theme_update(panel.grid.minor = element_blank()) + 
  scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile")) + 
  ylim(0,100)

bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  # filter(time < 100) %>% 
  ggplot(aes(method, time, color = method)) + 
  geom_jitter(width = 0.1) + 
  facet_wrap(vars(model), scales = "free_y") + 
  theme_update(panel.grid.minor = element_blank()) + 
  scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile"))

- First slide of strip charts
```{r}
first_eight <- bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  group_by(model) %>% 
  summarize(mean_time = mean(time)) %>% 
  arrange(mean_time) %>% 
  pull(model) %>% 
  .[1:8] %>% 
  sort()

first_six <- bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  group_by(model) %>% 
  summarize(mean_time = mean(time)) %>% 
  arrange(mean_time) %>% 
  pull(model) %>% 
  .[1:6] %>% 
  sort()

bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  filter(model %in% first_eight) %>% 
  filter(time < 100) %>% 
  ggplot(aes(method, time, color = method)) + 
  geom_jitter(width = 0.2, size = 1) + 
  # facet_wrap(vars(model), scales = "free_y") + 
  facet_wrap(vars(model)) + 
  theme_update(panel.grid.minor = element_blank()) + 
  scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile"))

bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  filter(model %in% first_six) %>% 
  filter(time < 100) %>% 
  ggplot(aes(method, time, color = method)) + 
  geom_jitter(width = 0.2) + 
  # facet_wrap(vars(model), scales = "free_y") + 
  facet_wrap(vars(model)) + 
  theme_update(panel.grid.minor = element_blank()) + 
  scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile"))

@@

```{r}
bugs_fit_condense <- readRDS(here("Simulation Results", "simple-models", 
                                  "discrete", "binomial", "beta-prior", 
                                  "bugs_fit_condense_beta_binomial.RDS"))
jags_fit_condense <- readRDS(here("Simulation Results", "simple-models", 
                                  "discrete", "binomial", "beta-prior", 
                                  "jags_fit_condense_beta_binomial.RDS"))
stan_fit_condense <- readRDS(here("Simulation Results", "simple-models", 
                                  "discrete", "binomial", "beta-prior", 
                                  "stan_fit_condense_beta_binomial.RDS"))
greta_fit_condense <- readRDS(here("Simulation Results", "simple-models", 
                                  "discrete", "binomial", "beta-prior", 
                                  "greta_fit_condense_beta_binomial.RDS"))
nimble_fit_condense <- readRDS(here("Simulation Results", "simple-models", 
                                  "discrete", "binomial", "beta-prior", 
                                  "nimble_fit_condense_beta_binomial.RDS"))
dists <- tibble(
  x = c(bugs_fit_condense, jags_fit_condense, stan_fit_condense, 
        greta_fit_condense, nimble_fit_condense),
  method = c(rep("bugs", length(bugs_fit_condense)),
             rep("jags", length(jags_fit_condense)),
             rep("stan", length(stan_fit_condense)),
             rep("greta", length(greta_fit_condense)),
             rep("nimble", length(nimble_fit_condense))
             )
)

dists %>% 
  ggplot(aes(x, color = method)) + 
  geom_density(adjust = 2) + 
  stat_function(fun = dbeta, args = list(3,9), color = "black")

tibble(x = bugs_fit_condense) %>% 
  ggplot(aes(x)) + 
    geom_density(adjust = 2) + 
    stat_function(fun = dbeta, args = list(3,9), color = "red")

tibble(x = jags_fit_condense) %>% 
  ggplot(aes(x)) + 
    geom_density(adjust = 2) + 
    stat_function(fun = dbeta, args = list(3,9), color = "red")

tibble(x = stan_fit_condense) %>% 
  ggplot(aes(x)) + 
    geom_density(adjust = 2) + 
    stat_function(fun = dbeta, args = list(3,9), color = "red")

```{r}
readRDS(here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-accuracy.rds"))

exp_gamma_acc_files <- c(
  here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-accuracy.rds"),
  here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-accuracy-nimble.rds")
)

@@

normal_normal_acc_files <- c(
  here("Simulation Results", "simple-models", "continuous", "normal", "normal-prior", "normal-normal-accuracy.rds")
  # here("Simulation Results", "simple-models", "continuous", "normal", "normal-prior", "normal-normal-accuracy-nimble.rds")
)

@@

  stan_mean <- combined_results$stan_dist %>% mean()

@@

exp_gamma_acc_df <- exp_gamma_acc_files %>% 
  combine_time_indiv("exponential_gamma")
normal_gamma_tau_acc_df <- normal_gamma_tau_acc_files %>% 
  combine_time_indiv("normal_gamma_tau")
# normal_normal_acc_df <- normal_normal_acc_files %>% 
#   combine_time_indiv("normal_normal")
beta_bernoulli_acc_df <- beta_bernoulli_acc_files %>% 
  combine_time_indiv("beta_bernoulli")
beta_binomial_acc_df <- beta_binomial_acc_files %>% 
  combine_time_indiv("beta_binomial")
poisson_gamma_acc_df <- poisson_gamma_acc_files %>% 
  combine_time_indiv("poisson_gamma")

time_results <- bind_rows(
  exp_gamma_acc_df,
  normal_gamma_tau_acc_df,
  beta_bernoulli_acc_df,
  beta_binomial_acc_df,
  poisson_gamma_acc_df
)

time_results %>% 
  pivot_longer(
    # cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist), 
    cols = c(JAGS, OpenBUGS, Stan, Nimble, Greta), 
    names_to = "method",
    values_to = "TVD_Ratio"
  ) %>% 
  ggplot(aes(TVD_Ratio)) + 
    geom_histogram(aes(fill = method)) + 
    facet_wrap(facets = "method") + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5),
        text = element_text(size=20)) + 
  ggtitle("Implementation TVD Accuracy Histograms") + 
  xlab("Implementation") + 
  ylab("TVD Ratio")

time_results %>% 
  pivot_longer(
    # cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist), 
    cols = c(JAGS, OpenBUGS, Stan, Nimble, Greta), 
    names_to = "method",
    values_to = "TVD_Ratio"
  ) %>% 
  ggplot(aes(x = method, y = TVD_Ratio)) + 
    geom_boxplot(aes(color = method), size = 0.7) + 
  ggtitle("Implementation TVD Accuracy Boxplots") + 
  xlab("Implementation") + 
  ylab("TVD Ratio") + 
  scale_x_discrete(limits = c("OpenBUGS", "JAGS", "Nimble", "Stan", "Greta")) + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5),
        text = element_text(size=20))

@@

## Strip charts for accuracy

```{r}
time_results
```

>>>>

---
title: "Simulation Results"
author: "Evan Miyakawa"
output:
  html_document:
    df_print: paged
---

@@

```{r, eval = FALSE}
exp_gamma_bench_files <- c(
  here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-results.rds"),
  here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-results-greta.rds"),
  here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-results-stan.rds")
)

@@

```{r, eval = FALSE}
# bench_results <- bind_rows(
#   exp_gamma_results,
#   normal_gamma_tau_results,
#   normal_normal_results,
#   beta_bernoulli_results, 
#   beta_binomial_results,
#   poisson_gamma_results,
#   hier_beta_binomial_results,
#   hier_full_bb_results,
#   hier_log_reg_results,
#   linear_reg_results,
#   logistic_reg_results,
#   poisson_reg_results
# )
# 
# bench_results
# 
# saveRDS(bench_results, file = "bench_results.RDS")

@@

saveRDS(bench_results_indiv, file = "bench_results_indiv.RDS")
# saveRDS(bench_results_indiv, file = "bench_results_indiv2.RDS")
```

@@

<!-- ## Strip Charts -->

<!-- ```{r} -->
<!-- bench_results_indiv %>%  -->
<!--   mutate(model = model_name %>%  -->
<!--            str_replace_all("_", " ")) %>%  -->
<!--   ggplot(aes(method, time)) +  -->
<!--   geom_jitter(width = 0.1) +  -->
<!--   facet_wrap(vars(model)) +  -->
<!--   theme_update(panel.grid.minor = element_blank()) +  -->
<!--   scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile")) +  -->
<!--   ylim(0,100) -->

<!-- bench_results_indiv %>%  -->
<!--   mutate(model = model_name %>%  -->
<!--            str_replace_all("_", " ")) %>%  -->
<!--   # filter(time < 100) %>%  -->
<!--   ggplot(aes(method, time, color = method)) +  -->
<!--   geom_jitter(width = 0.1) +  -->
<!--   facet_wrap(vars(model), scales = "free_y") +  -->
<!--   theme_update(panel.grid.minor = element_blank()) +  -->
<!--   scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile")) -->

<!-- ``` -->

<!-- - First slide of strip charts -->
<!-- ```{r} -->
<!-- first_nine <- bench_results_indiv %>%  -->
<!--   mutate(model = model_name %>%  -->
<!--            str_replace_all("_", " ")) %>%  -->
<!--   group_by(model) %>%  -->
<!--   summarize(mean_time = mean(time)) %>%  -->
<!--   arrange(mean_time) %>%  -->
<!--   pull(model) %>%  -->
<!--   .[1:9] %>%  -->
<!--   sort() -->

<!-- # first_six <- bench_results_indiv %>%  -->
<!-- #   mutate(model = model_name %>%  -->
<!-- #            str_replace_all("_", " ")) %>%  -->
<!-- #   group_by(model) %>%  -->
<!-- #   summarize(mean_time = mean(time)) %>%  -->
<!-- #   arrange(mean_time) %>%  -->
<!-- #   pull(model) %>%  -->
<!-- #   .[1:6] %>%  -->
<!-- #   sort() -->

<!-- bench_results_indiv %>%  -->
<!--   mutate(model = model_name %>%  -->
<!--            str_replace_all("_", " ")) %>%  -->
<!--   filter(model %in% first_nine) %>%  -->
<!--   filter(time < 100) %>%  -->
<!--   ggplot(aes(method, time, color = method)) +  -->
<!--   geom_jitter(width = 0.2, size = 1) +  -->
<!--   # facet_wrap(vars(model), scales = "free_y") +  -->
<!--   facet_wrap(vars(model)) +  -->
<!--   theme_update(panel.grid.minor = element_blank()) +  -->
<!--   scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile")) +  -->
<!--   labs(title = "Completion Time Strip Charts", subtitle = "Each individual simulation computation completion time shown, facetted by model") +  -->
<!--   theme(plot.title = element_text(hjust = 0.5, size = 20),  -->
<!--         plot.subtitle = element_text(hjust = 0.5),  -->
<!--         legend.position = "none",  -->
<!--         axis.text = element_text(size=10),  -->
<!--         axis.title = element_text(size = 13),  -->
<!--         axis.title.x = element_text(vjust = -1), -->
<!--         axis.title.y = element_text(vjust = 2))  +  -->
<!--   xlab("Implementation") +  -->
<!--   ylab("Completion Time") -->

<!-- # bench_results_indiv %>%  -->
<!-- #   mutate(model = model_name %>%  -->
<!-- #            str_replace_all("_", " ")) %>%  -->
<!-- #   filter(model %in% first_six) %>%  -->
<!-- #   filter(time < 100) %>%  -->
<!-- #   ggplot(aes(method, time, color = method)) +  -->
<!-- #   geom_jitter(width = 0.2) +  -->
<!-- #   # facet_wrap(vars(model), scales = "free_y") +  -->
<!-- #   facet_wrap(vars(model)) +  -->
<!-- #   theme_update(panel.grid.minor = element_blank()) +  -->
<!-- #   scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile")) -->

<!-- ``` -->

<!-- - second slide -->

<!-- ```{r} -->
<!-- last_seven <- bench_results_indiv %>%  -->
<!--   mutate(model = model_name %>%  -->
<!--            str_replace_all("_", " ")) %>%  -->
<!--   group_by(model) %>%  -->
<!--   summarize(mean_time = mean(time)) %>%  -->
<!--   arrange(mean_time) %>%  -->
<!--   pull(model) %>%  -->
<!--   .[10:16] %>%  -->
<!--   sort() -->

<!-- bench_results_indiv %>%  -->
<!--   mutate(model = model_name %>%  -->
<!--            str_replace_all("_", " ")) %>%  -->
<!--   filter(model %in% last_seven) %>%  -->
<!--   filter(time < 100) %>%  -->
<!--   ggplot(aes(method, time, color = method)) +  -->
<!--   geom_jitter(width = 0.2, size = 1) +  -->
<!--   # facet_wrap(vars(model), scales = "free_y") +  -->
<!--   facet_wrap(vars(model)) +  -->
<!--   theme_update(panel.grid.minor = element_blank()) +  -->
<!--   scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile")) +  -->
<!--   labs(title = "Completion Time Strip Charts", subtitle = "Each individual simulation computation completion time shown, facetted by model") +  -->
<!--   theme(plot.title = element_text(hjust = 0.5, size = 20),  -->
<!--         plot.subtitle = element_text(hjust = 0.5),  -->
<!--         legend.position = "none",  -->
<!--         axis.text = element_text(size=10),  -->
<!--         axis.title = element_text(size = 13),  -->
<!--         axis.title.x = element_text(vjust = -1), -->
<!--         axis.title.y = element_text(vjust = 2))  +  -->
<!--   xlab("Implementation") +  -->
<!--   ylab("Completion Time") -->
<!-- ``` -->

@@

<!-- ```{r} -->
<!-- bugs_fit_condense <- readRDS(here("Simulation Results", "simple-models",  -->
<!--                                   "discrete", "binomial", "beta-prior",  -->
<!--                                   "bugs_fit_condense_beta_binomial.RDS")) -->
<!-- jags_fit_condense <- readRDS(here("Simulation Results", "simple-models",  -->
<!--                                   "discrete", "binomial", "beta-prior",  -->
<!--                                   "jags_fit_condense_beta_binomial.RDS")) -->
<!-- stan_fit_condense <- readRDS(here("Simulation Results", "simple-models",  -->
<!--                                   "discrete", "binomial", "beta-prior",  -->
<!--                                   "stan_fit_condense_beta_binomial.RDS")) -->
<!-- greta_fit_condense <- readRDS(here("Simulation Results", "simple-models",  -->
<!--                                   "discrete", "binomial", "beta-prior",  -->
<!--                                   "greta_fit_condense_beta_binomial.RDS")) -->
<!-- nimble_fit_condense <- readRDS(here("Simulation Results", "simple-models",  -->
<!--                                   "discrete", "binomial", "beta-prior",  -->
<!--                                   "nimble_fit_condense_beta_binomial.RDS")) -->
<!-- dists <- tibble( -->
<!--   x = c(bugs_fit_condense, jags_fit_condense, stan_fit_condense,  -->
<!--         greta_fit_condense, nimble_fit_condense), -->
<!--   method = c(rep("bugs", length(bugs_fit_condense)), -->
<!--              rep("jags", length(jags_fit_condense)), -->
<!--              rep("stan", length(stan_fit_condense)), -->
<!--              rep("greta", length(greta_fit_condense)), -->
<!--              rep("nimble", length(nimble_fit_condense)) -->
<!--              ) -->
<!-- ) -->

<!-- dists %>%  -->
<!--   ggplot(aes(x, color = method)) +  -->
<!--   geom_density(adjust = 2) +  -->
<!--   stat_function(fun = dbeta, args = list(3,9), color = "black") -->

<!-- tibble(x = bugs_fit_condense) %>%  -->
<!--   ggplot(aes(x)) +  -->
<!--     geom_density(adjust = 2) +  -->
<!--     stat_function(fun = dbeta, args = list(3,9), color = "red") -->

<!-- tibble(x = jags_fit_condense) %>%  -->
<!--   ggplot(aes(x)) +  -->
<!--     geom_density(adjust = 2) +  -->
<!--     stat_function(fun = dbeta, args = list(3,9), color = "red") -->

<!-- tibble(x = stan_fit_condense) %>%  -->
<!--   ggplot(aes(x)) +  -->
<!--     geom_density(adjust = 2) +  -->
<!--     stat_function(fun = dbeta, args = list(3,9), color = "red") -->

<!-- ``` -->

```{r}
exp_gamma_acc_files <- c(
  here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-accuracy.rds"),
  here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-accuracy-nimble.rds")
)

@@

normal_normal_acc_files <- c(
  here("Simulation Results", "simple-models", "continuous", "normal", "normal-prior", "normal-normal-accuracy.rds"),
  here("Simulation Results", "simple-models", "continuous", "normal", "normal-prior", "normal-normal-accuracy-nimble.rds")
)

@@

  # stan_mean <- combined_results$stan_dist %>% mean()
  stan_mean <- 1

@@

exp_gamma_acc_df <- exp_gamma_acc_files %>% 
  combine_time_indiv("exponential_gamma")
normal_gamma_tau_acc_df <- normal_gamma_tau_acc_files %>% 
  combine_time_indiv("normal_gamma_tau")
normal_normal_acc_df <- normal_normal_acc_files %>%
  combine_time_indiv("normal_normal")
beta_bernoulli_acc_df <- beta_bernoulli_acc_files %>% 
  combine_time_indiv("beta_bernoulli")
beta_binomial_acc_df <- beta_binomial_acc_files %>% 
  combine_time_indiv("beta_binomial")
poisson_gamma_acc_df <- poisson_gamma_acc_files %>% 
  combine_time_indiv("poisson_gamma")

time_results <- bind_rows(
  exp_gamma_acc_df,
  normal_gamma_tau_acc_df,
  normal_normal_acc_df,
  beta_bernoulli_acc_df,
  beta_binomial_acc_df,
  poisson_gamma_acc_df
)
# 
# time_results %>% 
#   pivot_longer(
#     # cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist), 
#     cols = c(JAGS, OpenBUGS, Stan, Nimble, Greta), 
#     names_to = "method",
#     values_to = "TVD"
#   ) %>% 
#   ggplot(aes(TVD)) + 
#     geom_histogram(aes(fill = method)) + 
#     facet_wrap(facets = "method") + 
#   theme(legend.position="none",
#         plot.title = element_text(hjust = 0.5),
#         text = element_text(size=20)) + 
#   ggtitle("Implementation TVD Accuracy Histograms") + 
#   xlab("Implementation") + 
#   ylab("TVD Ratio")
# 
# time_results %>% 
#   pivot_longer(
#     # cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist), 
#     cols = c(JAGS, OpenBUGS, Stan, Nimble, Greta), 
#     names_to = "method",
#     values_to = "TVD_Ratio"
#   ) %>% 
#   ggplot(aes(x = method, y = TVD_Ratio)) + 
#     geom_boxplot(aes(color = method), size = 0.7) + 
#   ggtitle("Implementation TVD Accuracy Boxplots") + 
#   xlab("Implementation") + 
#   ylab("TVD Ratio") + 
#   scale_x_discrete(limits = c("OpenBUGS", "JAGS", "Nimble", "Stan", "Greta")) + 
#   theme(legend.position="none",
#         plot.title = element_text(hjust = 0.5),
#         text = element_text(size=20))

@@

## Strip charts for time

- First slide of strip charts
```{r}
first_nine <- bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  group_by(model) %>% 
  summarize(mean_time = mean(time)) %>% 
  arrange(mean_time) %>% 
  pull(model) %>% 
  .[1:9] %>% 
  sort()

# first_six <- bench_results_indiv %>% 
#   mutate(model = model_name %>% 
#            str_replace_all("_", " ")) %>% 
#   group_by(model) %>% 
#   summarize(mean_time = mean(time)) %>% 
#   arrange(mean_time) %>% 
#   pull(model) %>% 
#   .[1:6] %>% 
#   sort()

bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  filter(model %in% first_nine) %>% 
  filter(time < 100) %>% 
  ggplot(aes(method, time, color = method)) + 
  geom_jitter(width = 0.2, size = 1) + 
  # facet_wrap(vars(model), scales = "free_y") + 
  facet_wrap(vars(model)) + 
  theme_update(panel.grid.minor = element_blank()) + 
  scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile")) + 
  labs(title = "Completion Time Strip Charts", subtitle = "Each individual simulation computation completion time shown, facetted by model") + 
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        plot.subtitle = element_text(hjust = 0.5), 
        legend.position = "none", 
        axis.text = element_text(size=10), 
        axis.title = element_text(size = 13), 
        axis.title.x = element_text(vjust = -1),
        axis.title.y = element_text(vjust = 2))  + 
  xlab("Implementation") + 
  ylab("Completion Time (Seconds)")

# bench_results_indiv %>% 
#   mutate(model = model_name %>% 
#            str_replace_all("_", " ")) %>% 
#   filter(model %in% first_six) %>% 
#   filter(time < 100) %>% 
#   ggplot(aes(method, time, color = method)) + 
#   geom_jitter(width = 0.2) + 
#   # facet_wrap(vars(model), scales = "free_y") + 
#   facet_wrap(vars(model)) + 
#   theme_update(panel.grid.minor = element_blank()) + 
#   scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile"))

- second slide

```{r}
last_seven <- bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  group_by(model) %>% 
  summarize(mean_time = mean(time)) %>% 
  arrange(mean_time) %>% 
  pull(model) %>% 
  .[10:16] %>% 
  sort()

bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  filter(model %in% last_seven) %>% 
  filter(time < 100) %>% 
  ggplot(aes(method, time, color = method)) + 
  geom_jitter(width = 0.2, size = 1) + 
  # facet_wrap(vars(model), scales = "free_y") + 
  facet_wrap(vars(model)) + 
  theme_update(panel.grid.minor = element_blank()) + 
  scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile")) + 
  labs(title = "Completion Time Strip Charts", subtitle = "Each individual simulation computation completion time shown, facetted by model") + 
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        plot.subtitle = element_text(hjust = 0.5), 
        legend.position = "none", 
        axis.text = element_text(size=10), 
        axis.title = element_text(size = 13), 
        axis.title.x = element_text(vjust = -1),
        axis.title.y = element_text(vjust = 2))  + 
  xlab("Implementation") + 
  ylab("Completion Time (Seconds)")
```

- overall boxplot time

```{r}
bench_results_indiv %>% 
  mutate(model = model_name %>% 
           str_replace_all("_", " ")) %>% 
  filter(time < 100) %>% 
  ggplot(aes(method, time, color = method)) + 
  # geom_jitter(width = 0.2, size = 1) + 
  geom_boxplot() + 
  # facet_wrap(vars(model), scales = "free_y") + 
  # facet_wrap(vars(model)) + 
  theme_update(panel.grid.minor = element_blank()) + 
  scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan",  "Nimble", "Greta", "Stan Compile")) + 
  labs(title = "Completion Time Overall Boxplots", subtitle = "Completion time aggregated across all models, for each implementation") + 
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        plot.subtitle = element_text(hjust = 0.5), 
        legend.position = "none", 
        axis.text = element_text(size=10), 
        axis.title = element_text(size = 13), 
        axis.title.x = element_text(vjust = -1),
        axis.title.y = element_text(vjust = 2))  + 
  xlab("Implementation") + 
  ylab("Completion Time (Seconds)")
```

- first chart accuracy
```{r}
time_results %>% 
  pivot_longer(
    # cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist), 
    cols = c(JAGS, OpenBUGS, Stan, Nimble, Greta), 
    names_to = "method",
    values_to = "TVD"
  ) %>% 
  mutate(model = model %>% 
           str_replace_all("_", " ")) %>% 
  ggplot(aes(method, TVD, color = method)) + 
  geom_jitter(width = 0.1, size = 1) + 
  facet_wrap(vars(model)) +
  theme_update(panel.grid.minor = element_blank()) + 
  scale_x_discrete(limits = c("JAGS", "Stan", "Nimble", "OpenBUGS", "Greta")) + 
  xlab("Implementation") + 
   labs(title = "TVD Strip Charts", subtitle = "Each individual simulation TVD shown, facetted by model") + 
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        plot.subtitle = element_text(hjust = 0.5), 
        legend.position = "none", 
        axis.text = element_text(size=12), 
        axis.title = element_text(size = 15), 
        axis.title.x = element_text(vjust = -1),
        axis.title.y = element_text(vjust = 2))
```

- overall accuracy boxplot

```{r}
time_results %>% 
  pivot_longer(
    # cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist), 
    cols = c(JAGS, OpenBUGS, Stan, Nimble, Greta), 
    names_to = "method",
    values_to = "TVD"
  ) %>% 
  mutate(model = model %>% 
           str_replace_all("_", " ")) %>% 
  ggplot(aes(method, TVD, color = method)) + 
  # geom_jitter(width = 0.1, size = 1) + 
  geom_boxplot() + 
  # facet_wrap(vars(model)) +
  theme_update(panel.grid.minor = element_blank()) + 
  scale_x_discrete(limits = c("JAGS", "Stan", "Nimble", "OpenBUGS", "Greta")) + 
  xlab("Implementation") + 
  labs(title = "TVD Overall Boxplots", subtitle = "TVD aggregated across all models, for each implementation") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        plot.subtitle = element_text(hjust = 0.5), 
        legend.position = "none", 
        axis.text = element_text(size=12), 
        axis.title = element_text(size = 15), 
        axis.title.x = element_text(vjust = -1),
        axis.title.y = element_text(vjust = 2))

# time_results %>%
#   pivot_longer(
#     # cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist),
#     cols = c(JAGS, OpenBUGS, Stan, Nimble, Greta),
#     names_to = "method",
#     values_to = "TVD"
#   ) %>%
#   mutate(model = model %>%
#            str_replace_all("_", " ")) %>%
#   ggplot(aes(method, TVD, color = method)) +
#   # geom_jitter(width = 0.1, size = 1) +
#   geom_boxplot() +
#   # facet_wrap(vars(model)) +
#   theme_update(panel.grid.minor = element_blank()) +
#   scale_x_discrete(limits = c("JAGS", "Stan", "Nimble", "OpenBUGS", "Greta")) +
#   theme(
#     legend.position = "none"
#   ) +
#   xlab("Implementation") +
#   labs(title = "TVD Overall Boxplots", subtitle = "TVD aggregated across all models, for each implementation") +
#   theme(plot.title = element_text(hjust = 0.5),
#         plot.subtitle = element_text(hjust = 0.5))
#
